One more attempt on ArXe

### 2016-05-27 supp_theo_specs.tex
low xenon content clusters

\subsection{Clusters with $N=38$ Atoms of Different Composition}
Recently, structures for ArXe clusters of in total 38 atoms were optimized
using an evolutionary algorithm based on two-body potentials determined
by xyz. \cite{}
In this section, the simulated ICD and ETMD3 spectra for selected cluster
structures shown in Figure xyz of Ref. \citenum{} are shown in Figures
\ref{} -- \ref{} and discussed.

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar36Xe2.pdf}
 \caption{}
 \label{}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar34Xe4.pdf}
 \caption{}
 \label{}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar33Xe5.pdf}
 \caption{}
 \label{}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar14Xe24.pdf}
 \includegraphics[width=0.5\columnwidth]{pics/Ar13Xe25.pdf}
 \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
 \caption{Ar$_x$Xe$_y$ clusters with a xenon content of more than \unit[50]{\%}.
          The ETMD3 is the dominant processi for these cluster structures.
          They are shown for completeness but can, due to the high xenon content,
          not be related to the experimental secondary electron measurements.}
 \label{figure:ArXe_gt50}
\end{figure}

>>>>

\subsection{Clusters with $N=38$ Atoms of Different Composition}
Recently, structures for ArXe clusters of in total 38 atoms were optimized
using an evolutionary algorithm based on two-body potentials determined
by xyz. \cite{marques}
In this section, the simulated ICD and ETMD3 spectra for selected cluster
structures shown in Figure 7 of Ref. \citenum{marques} are shown in Figures
\ref{figure:ArXe_lt15} -- \ref{figure:ArXe_gt50} and discussed.

\begin{figure}
 \centering
 \includegraphics[width=0.32\columnwidth]{pics/Ar36Xe2.pdf}
 \includegraphics[width=0.32\columnwidth]{pics/Ar34Xe4.pdf}
 \includegraphics[width=0.32\columnwidth]{pics/Ar33Xe5.pdf}
 \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of
          \unit[5]{\%} to \unit[13]{\%}.
          According to our simulations the ETMD3 is the most prominent decay
          process for these cluster structures.
          In case of the Ar$_{36}$Xe$_2$ cluster only Xe-Xe distance is
          realized and therefore, the ETMD3 spectrum is very similar
          to one of a trimer
          showing two peaks originating
          from three different decay channels. In the other two cases the ETMD3
          spectrum is slightly more complex, but in all three cases, the ETMD3
          is manifested by peaks between \unit[0.5]{eV} and \unit[4.0]{eV} being
          in contrast to the experimental observations.}
 \label{figure:ArXe_lt15}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\columnwidth]{pics/Ar14Xe24.pdf}
 \includegraphics[width=0.5\columnwidth]{pics/Ar13Xe25.pdf}
 \includegraphics[width=0.5\columnwidth]{pics/Ar3Xe35.pdf}
 \caption{Ar$_N$Xe$_{38-N}$ clusters with a xenon content of more
          than \unit[50]{\%}.
          Our simulations show that ETMD3 is the dominant process
          for these cluster structures.
          They are shown for completeness but can, due to the high xenon content,
          not be related to the experimental secondary electron measurements.}
 \label{figure:ArXe_gt50}
\end{figure}
